\documentclass{curriculumVitae}

\title{\bfseries\Huge Owen Hempel}
\author{ohempel@hempeldesigngroup.com}
\date{}

\begin{document}

\maketitle

\vspace{1em}
\begin{minipage}[ht]{0.48\textwidth}
313 2nd Avenue East

Owen Sound, Ontario
\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
Cell: 226-668-8118
\end{minipage}


\section{Education}
\datedsubsection{McMaster University}{2011--Present}
I am currently pursuing a Bachelor of Engineering in Mechatronics Engineering at McMaster University. I have completed 3 years and an internship year, and am on schedule for graduation in spring 2016.

\datedsubsection{West Hill Secondary School}{2006--2011}
I achieved the Honour Roll and focused entirely on science and maths courses throughout high school.
\section{Special Skills}
\begin {itemize}
\item{Fluent in French}
\item{Experience in soldering and electronic circuit design} 
\item{Proficient with Autodesk Inventor CAD software}
\end{itemize}

\section{Work}
\datedsubsection{Bruce Power, Outage Maintenance Services/Reactor Tooling Design}{June 2014--August 2015}
Bruce Power is the world's largest nuclear operator and a 6,600 MW CANDU facility. It boasts close to 3,000 full time employees and a large number of contractors.

This was my first experience in the professional engineering world. I have gained an enormous amount of experience with professional work and general engineering. On top of that, I have received thorough training in a wide range of subjects. In particular, my work was related to systems design and integration of individual vendor products.

This has also allowed me to complete many courses of training I would otherwise not have had the opportunity to take. Some of these include radiation safety courses, extensive WHMIS courses, and more. My short time with Tool Engineering has been spent on a mixture of projects, which mainly revolve around maintaining or upgrading existing systems.

\datedsubsection{McMaster University, TA (Drafting)}{Sept 2013--April 2014}
This job has developed my ability to communicate with people who have less technical knowledge about a
particular subject. I have learned how to clearly communicate through language barriers, and
gained a proficiency in Autodesk Inventor Software.

 \datedsubsection{McMaster University, Learning Enrichment Advancement Program}{May 2013--August 2013}
 In this job, my co-worker and I were responsible for developing and delivering a curriculum of
engineering and science to high school aged students. This was a residential summer camp
based on science concepts. We were tasked with making projects that were challenging, but
not out of the realm of possibility, and also sticking to a limited budget. We covered
everything from basic electric circuits to programming and microcontrollers. This helped me
develop my skills in communicating science and engineering concepts in a relatable and
understandable way

 \datedsubsection{McMaster University, Facility Services}{Sept 2013--April 2014}

This job involved organization of a small team of custodians across several buildings, as well as
taking care of purchase orders and time sheets, and also secretarial duties. I worked with a
supervisor but this was almost entirely independent work. 

I also worked on the Grounds crew in the summer, which involved working in a crew to accomplish tasks as asked by Supervisors. Tasks range from
weeding and planting to installation of bicycle racks, paths, and gardens.
 
 \datedsubsection{Tim Hortons}{March 2010--August 2011}

In this job, I learned to work with a small team, and to serve a large number of customers and resolve issues quickly and efficiently. I gained strong proficiency in interpersonal skills and communication.
 
 \datedsubsection{Fremaco Devices, Inc}{Sept 2007--January 2010}

In this job I worked alone in a small-scale factory to produce, package, and ship a product. I learned how to maintain a schedule, to meet critical deadlines, and to work in a self-motivated environment.



\section {Volunteer History}
\datedsubsection {McMaster Engineering Musical- Film and archives/Crew}{2013-2014}
In my Engineering program's musical, we built set props and co-ordinated the scenes on stage. This involved many hours of work on weekends throughout the year, as well as a solid week of rehearsals all night after classes.
\datedsubsection {Mechatronics Engineering Sumobots club}{2013}
I participated in a school-wide sumobots-style robotics tournament. My participation was mainly administration and organizing the event, providing space for the teams to compete.

\datedsubsection {McMaster Engineering Society, First Year Representative (Elected position)}{2011}
I was elected by my classmates to represent them on the Engineer's Society. I was part of a functioning student government system, had to participate in bi-weekly meetings and vote regularly on issues in the engineering student society.
\datedsubsection {Owen Sound Little Theatre, Film and Archives}{2010}
In this position I filmed and created a movie of the local theatre group's production of Macbeth. I was in charge of the entire film and edit project. Rotary Club Seminar For Tomorrow's Leaders. I was selected as one of 150 identifiedleaders in Ontario, Michigan, and New York. I attended a 4-day seminar on leadership activities, team building, communication skills, and interpersonal relations. I learned how to form a cohesive team and participate in a positive way.
\datedsubsection {Beauty and the Beast, Film and Archives}{2009}
I filmed and created a movie of West Hill Secondary School's Musical theatre production. I was in charge of the entire project, and it was submitted as a final project for class. It was graded as 100\%.

\section {Other Interests and Extracurriculars}

\begin{itemize}
\item {FIRST Robotics Mentor, 2015 season (Team 781)}
\item {McMaster Engineering Social Committee}
\item {McMaster Engineering Rugby Squad (Captain)}
\item {McMaster Engineering Hockey club (Co-captain)}
\item {West Hill Cross Country running team, Captain in 2009}
\end{itemize}

\end{document} 